Spin canonical divisors of log stacky curves

### 2015-06-21 stacky_write_up/spin_cring.tex
minor edits to admissibilty, fix Peter's code

We will sketch a proof by induction.  O'Dorney \todo{Insert reference to Theorem 4} provides a base case when $D\sim \frac{\alpha}{\beta} P$.  He finds generators in degrees up to $\beta$ and relations that are all quadratic in the generators (and thus lying in degrees at most $2\beta$).  We can ind

@@

\begin{enumerate}
	\item[(Ad-i)] Suppose for all $i \in J$, there exists $y_{i,e_i'} 
		\in R'$ so that $R'$ admits a presentation
		\begin{align*}
			R' \cong \left( k[x] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
		\end{align*}
		so that for all $i \in J$ we have $\deg y_{e_i'} = e_i'$ and $-ord_{
		Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
	\item[(Ad-ii)] For all $i \in J$ and $z \neq y_{i,e_i'}$ a 
		generator of $R'$ we have
		\begin{align*}
			\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[(Ad-iii)] For all $i \in J$ we have for all $d \geq 0$,
		\begin{align*}
			\deg \lfloor e_i L \rfloor \geq \# S(i,d)
		\end{align*}
		where
		\begin{align*}
			S(i,d) = \{j \in J : j \neq i \text{ and }e_j'+2d \mid e_i+2d\}
		\end{align*}
\end{enumerate}
\end{defn}

@@

\begin{thm}
\label{thm:ramification_order_induction}
Suppose $(\sx', 0, L')$ is a tame separably rooted log stacky spin
curve is admissible with a generators $y_{i,e_i'} \in R' = R_{L'}$
as in (Ad-i) of Definition ~\ref{defn:admissible}. Then the
following are true:
\begin{enumerate}
	\item[(a)] For all $i \in J$, there exists $y_{i,e_i} \in
		H^0(\sx, e_i(K_\sx))$ so that
		\begin{align*}
			-ord_{Q_i}(y_{i,e_i}) = \frac{e_i-1}{2}
		\end{align*}
		and
		\begin{align*}
			\frac{-\ord_{Q_j}(y_{i,e_i'})}{y_{i,e_i}} \leq \subhalf{e_j'}-
			\frac{1}{\deg(y_{i,e_i'})e_j'}
		\end{align*}
		for all $j \in J$ with $j \neq i$.
	\item[(b)] The elements $y_{i,e_i'}^ay_{i,e_i}^b,$ with $a \geq 0,
		b > 0$ span $R$ over $R'$ and the elements $y_{i,e_i}$ minimally
		generate $R$ over $R'$.
	\item[(c)] Equip $k[y] = k[y_{i,e_i}]_{i \in J}$ and $k[x]$ with
		any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with
		block order. Let $R = k[y,x]/I.$ Then,
		\begin{align*}
			in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z \neq
			y_{i,e_i},y_{i,e_i'} \rangle
		\end{align*}
		as $z$ ranges over all generators of $R$.
	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
		products of two monomials and that for all $i \in J$, we have $e_i >
		\deg z$ for any generator $z$ of $R'.$ Then any set of minimal
		generators for $I'$ together with any set of relations as in part (c)
		minimally generate $I$.
	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
\end{enumerate}
\end{thm}

@@

Finally, if $(\sx,J)$ then so is $(\sx,W)$ for any $W \subset J$,
since each of the conditions (Ad-i), (Ad-ii), and (Ad-iii) hold for
$W$ if they hold for $J$.
\end{proof}

>>>>

We will prove this by induction using methods analogous to ones of VZB\todo{add reference}.  O'Dorney \todo{Insert reference to Theorem 4} provides a base case when $D\sim \frac{\alpha}{\beta} P$:
\begin{lem}\label{lem:O'Dorney_1_point}
Let 
\[
	0<\frac{c_1}{d_1}<\frac{c_2}{d_2}<...<\frac{c_r}{d_r}=\frac{\alpha}{\beta}
\] 
be the nonnegative best lower approximation\todo{define this above} of $\frac{\alpha}{\beta}$.  Then $R_D$ is generated up to degree $\beta$ by generators $y_1,...,y_r$ where $y_i$ lies in degree $d_i$ with pole of degree $c_i$ at $P$.  
\end{lem}
\begin{proof}
See O'Dorney \todo{provide reference}.
\end{proof}

The following lemma extends this as well as a lemma of VZB \todo{reference to lemma 8.3.1 in VZB} and provides a method to induct from this as well as many other base cases.

\begin{lem}
\label{lem:deg1_sat_ind}
Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as defined by O'Dorney\todo{reference this-Section 1 of Evan's paper}) satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a generator $u$ in degree 1; let $u$.  Suppose $D$ is generated by $u,x_1,...,x_m$ in degree at most $\delta$ with relations generated in degree at most $\tau$.  Suppose $D'=D+\frac{\alpha}{\beta}P$ for some $P\not\in \Supp(D), \alpha,\beta\in \mathbf{N}$ such that 
\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X,\lfloor{dD+d\frac{\alpha}{\beta}P\rfloor})=h^0(X,\lfloor dD
	\rfloor)+\lfloor d\frac{\alpha}{\beta}\rfloor \forall d\in \mathbf{N}:
	d\ge \frac{\beta}{\alpha}.
\end{equation}
Let 
\[
	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
\]
be the non-negative best lower approximation.
Then 
\begin{itemize}
\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  degree $d_i$ and has a pole at $P$ of degree $c_i$
\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then 
\begin{align*}
	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
										 &+ \langle y_i y_j: 1 \le i \le j \le n-1 \rangle.
\end{align*}
\todo{See if we can additionally get the other information discussed in VZB theorem 8.3.1}
\end{itemize}
\end{lem}

\begin{proof}
Observe that $u_D,x_1,...,x_m$ each of which has no pole at $P$.  These can be chosen generically to not have a zero at $P$ \todo{check that we can actually do this, or eliminate if it turns out to be unnecessary}.

Begin by focusing on the $d^{\text{th}}$ component of $R_{D'}$: $(R_
{D'})_d = H^0(X, \lfloor D + \frac{\alpha}{\beta} P \rfloor)$.  By our
hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d\in\mathbf{N}$ such that $\lfloor d\frac{
\alpha}{\beta}\rfloor>0$,

\[
	h^0 (X, d(D+\frac{\alpha}{\beta})) = h^0(X, dD) + \deg(d\frac{\alpha}{\beta})
\]

\noindent
so in $H^0 (X, \lfloor dD' \rfloor)$ we can find elements with pole
order $i$ at $P$ for any $i \in \{0, \ldots, \lfloor d \frac{\alpha}{
\beta} \rfloor \}$. We can use a method similar to O'Dorney to
construct the $y_i$'s as desired: \todo{cite where}

Let $0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{
\beta}$ be the non-negative best lower approximation of $\frac{
\alpha}{\beta}$.  Note that elements of $H^0(X,dD')$ have pole of
orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
c_i $ at $P$.  For any $j < i$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$
by construction, so any product of $\prod z_i$ of elements of
degrees less than $d_i$ must have $\frac{-\ord(z_i)}{\deg(z_i)} <
\frac{c_i}{d _i}$, so we have the pole order of this product is $
\sum -\ord(z_i) = d_i(\frac{\sum -\ord( z_i)}{\sum \deg( z_i)}) < d_
i\frac{c_i}{d_i} = c_i $. Thus, the elements of $R_{d_i}$

In fact, a generic element in the respective degree will suffice.
\todo{add proof of this; is the generic statement correct?}
Following the argument given by O'Dorney \todo{cite, give specific
theorem number} correctly gives that these along with $u$ (in
degree 1 with 0 pole at $P$) generate a $\lfloor d\frac{ \alpha}{
\beta}\rfloor+1$ dimension $k$-vector space inside of $(R_{ D'})_d$
with a $\lfloor d\frac{\alpha}{\beta}\rfloor$ dimensional subspace
consisting of elements only with nonzero pole at $P$. Therefore, by
pole considerations $y_1,...,y_n$ generate $(R_{D'})_d $ over $(R_{D
})_d$, \todo{the word generate here is a little imprecise} so $u,x_1
,...,x_m,y_1,...,y_n$ generate $R_{D'}$.

@@

\begin{enumerate}
	\item[(Ad-i)] Suppose for all $i \in J$, there exists $y_{i,e_i'} 
		\in R'$ so that $R'$ admits a presentation
		\begin{align*}
			R' \cong \left( k[x] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
		\end{align*}
		so that for all $i \in J$ we have $\deg y_{e_i'} = e_i'$ and $-ord_{
		Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
	\item[(Ad-ii)] For all $i \in J$, any generator $z \neq y_{i,e_i'}$
		of $R'$ satisfies
		\begin{align*}
			\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[(Ad-iii)] For all $i \in J$ we have
		\begin{align*}
			\deg \lfloor e_i L \rfloor \geq \# S(i)
		\end{align*}
		where
		\begin{align*}
			S(i) := \{j \in J : j \neq i \text{ and } e_j'+2d \mid e_i -
			e_j' \text{ for some } d \geq 0\}
		\end{align*}
\end{enumerate}
\end{defn}

@@

\begin{lem}
\label{lem:admissible_subset}
If $(\sx', J)$ is admissible and $W \subset J$ is any subset,
then $(\sx', W)$ is also admissible.
\end{lem}

\begin{proof}
Each of the conditions (Ad-i), (Ad-ii), and (Ad-iii) hold for $W$
if they hold for $J$.
\end{proof}

\begin{thm}
\label{thm:ramification_order_induction}
Suppose $(\sx', 0, L')$ is a tame separably rooted log stacky spin
curve and $(\sx', J)$ is admissible with generators $y_{i,e_i'} \in
R' = R_{L'}$ as in (Ad-i) of Definition ~\ref{defn:admissible}.
Then the following are true:
\begin{enumerate}
	\item[(a)] For all $i \in J$, there exists $y_{i,e_i} \in
		H^0(\sx, e_i(K_\sx))$ so that
		\begin{align*}
			-ord_{Q_i}(y_{i,e_i}) = \frac{e_i-1}{2}
		\end{align*}
		and
		\begin{align*}
			\frac{-\ord_{Q_j}(y_{i,e_i'})}{y_{i,e_i}} \leq \subhalf{e_j'}-
			\frac{1}{\deg(y_{i,e_i'})e_j'}
		\end{align*}
		for all $j \in J$ with $j \neq i$.
	\item[(b)] The elements $y_{i,e_i'}^ay_{i,e_i}^b,$ with $a \geq 0,
		b > 0$ span $R$ over $R'$ and the elements $y_{i,e_i}$ minimally
		generate $R$ over $R'$.
	\item[(c)] Equip $k[y] = k[y_{i,e_i}]_{i \in J}$ and $k[x]$ with
		any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with
		block order. Let $R = k[y,x]/I.$ Then,
		\begin{align*}
			in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z 
			\neq y_{i,e_i},y_{i,e_i'} \rangle
		\end{align*}
		as $z$ ranges over all generators of $R$.
	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
		products of two monomials and that for all $i \in J$, we have $e
		_i > \deg z$ for any generator $z$ of $R'.$ Then any set of
		minimal generators for $I'$ together with any set of relations as in 
		part (c) minimally generate $I$.
	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
\end{enumerate}
\end{thm}

@@

Finally, if $(\sx, J)$ is admissible then so is $(\sx,W)$ for any
$W \subset J$ by Lemma ~\ref{lem:admissible_subset}.
\end{proof}
